Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-02 SupportingInformation.Rmd
minor edit

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
source("mtime.R") #A function needed for caching
library(captioner)
library(parallel)
busycores<-detectCores()-2 # for parallell computing with mclapply your computer will use all cores except two.
```

>>>>

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
source("mtime.R") #A function needed for caching
library(captioner)
library(parallel)
freecores<-2
busycores<-detectCores()-freecores # for parallell computing with mclapply your computer will use all cores except the number of freecores.
```
